---
title: "Cuebiq City Comparisons"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/Desktop/Thesis')
library(ggplot2)
library(dplyr)
library(tidyr)
# install.packages("stargazer")
library(stargazer)
library(jtools)
library(ggrepel)
library(cowplot)
```

```{r}
rm(list = ls())
cuebiq_data = read.csv("Data/working/cuebiq_zip.csv")
data = read.csv("Data/working/data_merged_zip.csv")
cbsa = read.csv("Data/raw/cbsa2fipsxw.csv")
```

# Get aggregated experienced segregation for every zip
```{r}
cuebiq_data$bias <- ((cuebiq_data$p1a + cuebiq_data$p2a) - (cuebiq_data$p3a + cuebiq_data$p4a))^2

cols = cuebiq_data %>% select(
  postcode,
  nstays,
  segregation,
  bias
)

zips <- cols %>% 
  group_by(postcode) %>% 
  summarize(across(c(segregation, bias),function (x) weighted.mean(x, w=nstays, na.rm=TRUE)))

zips_nstays <- cols %>% 
  group_by(postcode) %>% 
  summarize_at(vars(nstays), funs(mean))

# Accounts for DC/Maryland & Virginia issue
# data[data$state_fips == 24,]$state_fips = 11
# data[data$state_fips == 51,]$state_fips = 11

zips <- rename(zips, "zip" = "postcode")
zips$zip = as.integer(zips$zip)
zips_nstays <- rename(zips_nstays, "zip" = "postcode")
zips_nstays$zip = as.integer(zips_nstays$zip)

zips <- zips %>%
  inner_join(data, by = c("zip"))

zips_nstays <- zips_nstays %>%
  left_join(data, by = c("zip"))
```

#Standardize all variables
```{r}
zips$segregation = scale(zips$segregation)
zips$bias_grp_mem_zip = scale(zips$bias_grp_mem_zip)
zips$D3B = scale(zips$D3B)
zips$D2B_E8MIXA = scale(zips$D2B_E8MIXA)
zips$D1C8_ENT = scale(zips$D1C8_ENT)
zips$population_density = scale(zips$population_density)
zips$pop2018 = scale(zips$pop2018)
zips$median_household_income = scale(zips$median_household_income)
zips$diversity = scale(zips$diversity)
zips$college_rates = scale(zips$college_rates)
zips$unemployment_rate = scale(zips$unemployment_rate)
```

# Get combined urban form measure
```{r}

```

# PCA
```{r}
urban_form_measures <- zips %>% select(D1C8_ENT, D3B, D2B_E8MIXA)

# Run PCA on the selected columns
urban_form_pca <- prcomp(urban_form_measures, scale = TRUE)

# Extract the first principal component as the composite measure
urban_form_composite <- urban_form_pca$x[,1]

zips$urban_form <- urban_form_composite
```

# Factor analysis
```{r}

```

# Match each zip code to a CBSA
```{r}
df <- select(cbsa, fipscountycode, fipsstatecode, cbsatitle)
df <- rename(df, "county_code" = "fipscountycode")
df <- rename(df, "Geo_STATE" = "fipsstatecode")


zips$county_code <- zips$county %% 1000


zips <- zips %>%
  left_join(df, by = c("county_code", "Geo_STATE"))


# BOSTON
zips$cbsatitle[zips$cbsatitle == "Barnstable Town, MA"] <- "Boston-Cambridge-Newton, MA-NH"
zips$cbsatitle[zips$cbsatitle == "Manchester-Nashua, NH"] <- "Boston-Cambridge-Newton, MA-NH"
zips$cbsatitle[zips$cbsatitle == "Worcester, MA-CT"] <- "Boston-Cambridge-Newton, MA-NH"
zips$cbsatitle[zips$cbsatitle == "Providence-Warwick, RI-MA"] <- "Boston-Cambridge-Newton, MA-NH"
zips$cbsatitle[zips$cbsatitle == "Portland-South Portland, ME"] <- "Boston-Cambridge-Newton, MA-NH"

# NYC
zips$cbsatitle[zips$cbsatitle == "Bridgeport-Stamford-Norwalk, CT"] <- "New York-Newark-Jersey City, NY-NJ-PA"
zips$cbsatitle[zips$cbsatitle == "Kingston, NY"] <- "New York-Newark-Jersey City, NY-NJ-PA"

# PHILLY
zips$cbsatitle[zips$cbsatitle == "Atlantic City-Hammonton, NJ"] <- "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD"
zips$cbsatitle[zips$cbsatitle == "Allentown-Bethlehem-Easton, PA-NJ"] <- "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD"
zips$cbsatitle[zips$cbsatitle == "Trenton, NJ"] <- "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD"
zips$cbsatitle[zips$cbsatitle == "Lancaster, PA"] <- "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD"

# DC
zips$cbsatitle[zips$cbsatitle == "Baltimore-Columbia-Towson, MD"] <- "Washington-Arlington-Alexandria, DC-VA-MD-WV"
zips$cbsatitle[zips$cbsatitle == "Dover, DE"] <- "Washington-Arlington-Alexandria, DC-VA-MD-WV"
zips$cbsatitle[zips$cbsatitle == "Richmond, VA"] <- "Washington-Arlington-Alexandria, DC-VA-MD-WV"
zips$cbsatitle[zips$cbsatitle == "Winchester, VA-WV"] <- "Washington-Arlington-Alexandria, DC-VA-MD-WV"

# CHICAGO
zips$cbsatitle[zips$cbsatitle == "Michigan City-La Porte, IN"] <- "Chicago-Naperville-Elgin, IL-IN-WI"
zips$cbsatitle[zips$cbsatitle == "Racine, WI"] <- "Chicago-Naperville-Elgin, IL-IN-WI"
zips$cbsatitle[zips$cbsatitle == "Ottawa-Peru, IL" ] <- "Chicago-Naperville-Elgin, IL-IN-WI"
zips$cbsatitle[zips$cbsatitle == "Pontiac, IL"] <- "Chicago-Naperville-Elgin, IL-IN-WI"
zips$cbsatitle[zips$cbsatitle == "Kankakee, IL"] <- "Chicago-Naperville-Elgin, IL-IN-WI"

# DETROIT
zips$cbsatitle[zips$cbsatitle == "Ann Arbor, MI"] <- "Detroit-Warren-Dearborn, MI"
zips$cbsatitle[zips$cbsatitle == "Flint, MI"] <- "Detroit-Warren-Dearborn, MI"

# DALLAS 
zips$cbsatitle[zips$cbsatitle == "Athens, TX"] <- "Dallas-Fort Worth-Arlington, TX"
zips$cbsatitle[zips$cbsatitle == "Mineral Wells, TX"] <- "Dallas-Fort Worth-Arlington, TX"

# LOS ANGELES
zips$cbsatitle[zips$cbsatitle == "Oxnard-Thousand Oaks-Ventura, CA"] <- "Los Angeles-Long Beach-Anaheim, CA"
zips$cbsatitle[zips$cbsatitle == "Riverside-San Bernardino-Ontario, CA"] <- "Los Angeles-Long Beach-Anaheim, CA"
zips$cbsatitle[zips$cbsatitle == "Bakersfield, CA" ] <- "Los Angeles-Long Beach-Anaheim, CA"

# SAN FRANCISCO
zips$cbsatitle[zips$cbsatitle == "San Jose-Sunnyvale-Santa Clara, CA"  ] <- "San Francisco-Oakland-Hayward, CA"

# SEATTLE
zips$cbsatitle[zips$cbsatitle == "Oak Harbor, WA"] <- "Seattle-Tacoma-Bellevue, WA"
zips$cbsatitle[zips$cbsatitle =="Bremerton-Silverdale, WA"] <- "Seattle-Tacoma-Bellevue, WA"

cbsas <- c(
  "New York-Newark-Jersey City, NY-NJ-PA",
  "Los Angeles-Long Beach-Anaheim, CA",
  "Chicago-Naperville-Elgin, IL-IN-WI",
  "Dallas-Fort Worth-Arlington, TX",
  "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD",
  "Washington-Arlington-Alexandria, DC-VA-MD-WV",
  "Miami-Fort Lauderdale-West Palm Beach, FL",
  "Boston-Cambridge-Newton, MA-NH",
  "San Francisco-Oakland-Hayward, CA",
  "Detroit-Warren-Dearborn, MI",
  "Seattle-Tacoma-Bellevue, WA"
)

zips <- subset(zips, cbsatitle %in% cbsas)

unique(zips$cbsatitle)

```

# Group by CBSA
```{r}
cols <- zips %>% select(
  cbsatitle,
  pop2018,
  D3B,
  D2B_E8MIXA,
  D1C8_ENT,
  segregation,
  # urban_form,
  bias_grp_mem_zip,
)

cities <- cols %>%
  group_by(cbsatitle) %>%
  summarize_at(vars(D3B:bias_grp_mem_zip),funs(weighted.mean(., w=pop2018, na.rm=TRUE)))

cities[cities$cbsatitle == "Boston-Cambridge-Newton, MA-NH",]$cbsatitle = "Boston"
cities[cities$cbsatitle == "Chicago-Naperville-Elgin, IL-IN-WI",]$cbsatitle = "Chicago"
cities[cities$cbsatitle == "Dallas-Fort Worth-Arlington, TX",]$cbsatitle = "Dallas"
cities[cities$cbsatitle == "Detroit-Warren-Dearborn, MI",]$cbsatitle = "Detroit"
cities[cities$cbsatitle == "Los Angeles-Long Beach-Anaheim, CA",]$cbsatitle = "Los Angeles"
cities[cities$cbsatitle == "Miami-Fort Lauderdale-West Palm Beach, FL",]$cbsatitle = "Miami"
cities[cities$cbsatitle == "New York-Newark-Jersey City, NY-NJ-PA",]$cbsatitle = "New York City"
cities[cities$cbsatitle == "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD",]$cbsatitle = "Philadelphia"
cities[cities$cbsatitle == "Seattle-Tacoma-Bellevue, WA",]$cbsatitle = "Seattle"
cities[cities$cbsatitle == "San Francisco-Oakland-Hayward, CA",]$cbsatitle = "San Francisco"
cities[cities$cbsatitle == "Washington-Arlington-Alexandria, DC-VA-MD-WV",]$cbsatitle = "Washington"
```

```{r}
head(cities)
(cities[cities$cbsatitle == "Detroit",]$D3B - mean(cities$D3B)) / mean(cities$D3B)
(cities[cities$cbsatitle == "Detroit",]$D3B - cities[cities$cbsatitle == "Los Angeles",]$D3B) / cities[cities$cbsatitle == "Los Angeles",]$D3B

(cities[cities$cbsatitle == "Detroit",]$D1C8_ENT - mean(cities$D1C8_ENT)) / mean(cities$D1C8_ENT)
(cities[cities$cbsatitle == "Detroit",]$D2B_E8MIXA - mean(cities$D2B_E8MIXA)) / mean(cities$D2B_E8MIXA)

(cities[cities$cbsatitle == "Detroit",]$segregation - mean(cities$segregation)) / mean(cities$segregation)
(cities[cities$cbsatitle == "Detroit",]$segregation - cities[cities$cbsatitle == "Seattle",]$segregation) / cities[cities$cbsatitle == "Seattle",]$segregation


```

```{r}
cities$urban_form2 = (scale(cities$D3B) + scale(cities$D2B_E8MIXA) + scale(cities$D1C8_ENT))/3
```

```{r}
test <- subset(cities, cbsatitle == "Washington")
test$D3B

test2 <- subset(cities, cbsatitle == "Detroit")
test2$D3B
```


# Plot all cities (Urban Form vs Segregation)
```{r}
ggplot(cities, aes(x = D2B_E8MIXA, y = segregation)) +
  geom_point(color="magenta", size=3) +
  geom_label_repel(aes(label = cbsatitle),
                    fill="darkblue", color = 'white',
                    size = 4) +
  geom_smooth(method="lm", formula=y~x) +
  xlab("Urban Form") + 
  ylab("Experienced Economic Segregation")

# ggsave("cities_urban_form_vs_segregation_plot.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

# Plot all cities (Segregation vs Bias)
```{r}
ggplot(cities, aes(x = segregation, y = bias_grp_mem_zip)) +
  geom_point(color="magenta", size=3) +
  geom_label_repel(aes(label = cbsatitle),
                    fill="darkblue", color = 'white',
                    size = 4) +
  xlab("Experienced Economic Segregation") + 
  ylab("Friending Bias")

# ggsave("cities_segregation_vs_bias_plot.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
ggplot(zips, aes(x = segregation, y = bias_grp_mem_zip, color = cbsatitle)) +
  # geom_point( size=1, alpha=0.3) +
  geom_smooth(method='lm', formula=y~x) +
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=1, geom='point', alpha=0.2) +
  xlab("Experienced Economic Segregation") +
  ylab("Friending Bias") +
  facet_wrap(~cbsatitle)
```



```{r}
(cities[cities$cbsatitle == "Detroit",]$D3B - mean(cities$D3B))/sd(cities$D3B)
(cities[cities$cbsatitle == "Detroit",]$D1C8_ENT - mean(cities$D1C8_ENT))/sd(cities$D1C8_ENT)
(cities[cities$cbsatitle == "Detroit",]$D2B_E8MIXA - mean(cities$D2B_E8MIXA))/sd(cities$D2B_E8MIXA)

(cities[cities$cbsatitle == "Detroit",]$D2B_E8MIXA - cities[cities$cbsatitle == "San Francisco",]$D2B_E8MIXA)/sd(cities$D2B_E8MIXA)
(cities[cities$cbsatitle == "Detroit",]$D2B_E8MIXA - max(cities$D2B_E8MIXA))/sd(cities$D2B_E8MIXA)
(cities[cities$cbsatitle == "Detroit",]$D3B - max(cities$D3B))/sd(cities$D3B)
(cities[cities$cbsatitle == "Detroit",]$D1C8_ENT - max(cities$D1C8_ENT))/sd(cities$D1C8_ENT)


```


# Visualizing Intersection Density
```{r}
cities$D3B_z <- round((cities$D3B - mean(cities$D3B))/sd(cities$D3B), 2)  # compute normalized mpg
cities$D3B_flag <- ifelse(cities$D3B_z < 0, "below", "above")  # above / below avg flag
cities <- cities[order(cities$D3B_z), ]  # sort
cities$cbsatitle <- factor(cities$cbsatitle, levels = cities$cbsatitle)  # convert to factor to retain sorted order in plot.


ggplot(cities, aes(x=cbsatitle, y=D3B_z, label='Street Intersection Density')) + 
  geom_bar(stat='identity', aes(fill=D3B_flag), width=.5)  +
  scale_fill_manual(name="Street Intersection Density", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
  labs(title= "Intersection Density") + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size=12, face="bold"),
        legend.position = "none") +
  ylab("Intersection Density") +
  coord_flip()

# ggsave("city_rank_intersection_density.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs", width=5, height=4)

```

# Visualizing Entertainment Place Density
```{r}
cities$D1C8_ENT_z <- round((cities$D1C8_ENT - mean(cities$D1C8_ENT))/sd(cities$D1C8_ENT), 2)  # compute normalized mpg
cities$D1C8_ENT_flag <- ifelse(cities$D1C8_ENT_z < 0, "below", "above")  # above / below avg flag
cities <- cities[order(cities$D1C8_ENT_z), ]  # sort
cities$cbsatitle <- factor(cities$cbsatitle, levels = cities$cbsatitle)  # convert to factor to retain sorted order in plot.

ggplot(cities, aes(x=cbsatitle, y=D1C8_ENT_z, label='Entertainment Place Density')) + 
  geom_bar(stat='identity', aes(fill=D1C8_ENT_flag), width=.5)  +
  scale_fill_manual(name="Entertainment Place Density", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
   labs(title= "Entertainment Place Density") + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size=12, face="bold"),
        legend.position = "none") +
  ylab("Entertainment Place Density") +
  coord_flip()

ggsave("city_rank_entertainment_place_density.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs", width=5, height=4)
```

# Visualizing Employment Entropy
```{r}
cities$D2B_E8MIXA_z <- round((cities$D2B_E8MIXA - mean(cities$D2B_E8MIXA))/sd(cities$D2B_E8MIXA), 2)  # compute normalized mpg
cities$D2B_E8MIXA_flag <- ifelse(cities$D2B_E8MIXA_z < 0, "below", "above")  # above / below avg flag
cities <- cities[order(cities$D2B_E8MIXA_z), ]  # sort
cities$cbsatitle <- factor(cities$cbsatitle, levels = cities$cbsatitle)  # convert to factor to retain sorted order in plot.

ggplot(cities, aes(x=cbsatitle, y=D2B_E8MIXA_z, label='Employment Entropy')) + 
  geom_bar(stat='identity', aes(fill=D2B_E8MIXA_flag), width=.5)  +
  scale_fill_manual(name="Employment Entropy", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
   labs(title= "Employment Entropy") + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size=12, face="bold"),
        legend.position = "none") +
  ylab("Employment Entropy") +
  coord_flip()

# ggsave("city_rank_employment_entropy.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs", width=5, height=4)
```

# Visualizing Experienced Segregation
```{r}
cities$segregation_z <- round((cities$segregation - mean(cities$segregation))/sd(cities$segregation), 2)  # compute normalized mpg
cities$segregation_flag <- ifelse(cities$segregation_z < 0, "below", "above")  # above / below avg flag
cities <- cities[order(cities$segregation_z), ]  # sort
cities$cbsatitle <- factor(cities$cbsatitle, levels = cities$cbsatitle)  # convert to factor to retain sorted order in plot.

ggplot(cities, aes(x=cbsatitle, y=segregation_z, label='Experienced Segregation')) + 
  geom_bar(stat='identity', aes(fill=segregation_flag), width=.5)  +
  scale_fill_manual(name="Experienced Segregation", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#f8766d", "below"="#00ba38")) + 
   labs(title= "Experienced Segregation") + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size=12, face="bold"),
        legend.position = "none") +
  ylab("Experienced Segregation") +
  coord_flip()

ggsave("city_rank_segregation.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs", width=5, height=4)
```

# Visualizing Friending Bias
```{r}
cities$bias_grp_mem_zip_z <- round((cities$bias_grp_mem_zip - mean(cities$bias_grp_mem_zip))/sd(cities$bias_grp_mem_zip), 2)  # compute normalized mpg
cities$bias_grp_mem_zip_flag <- ifelse(cities$bias_grp_mem_zip_z < 0, "below", "above")  # above / below avg flag
cities <- cities[order(cities$bias_grp_mem_zip_z), ]  # sort
cities$cbsatitle <- factor(cities$cbsatitle, levels = cities$cbsatitle)  # convert to factor to retain sorted order in plot.

ggplot(cities, aes(x=cbsatitle, y=bias_grp_mem_zip_z, label='Friending Bias')) + 
  geom_bar(stat='identity', aes(fill=bias_grp_mem_zip_flag), width=.5)  +
  scale_fill_manual(name="Experienced Segregation", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#f8766d", "below"="#00ba38")) + #f8766d
   labs(title= "Friending Bias") + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_text(size=12, face="bold"),
        legend.position = "none") +
  ylab("Friending Bias") +
  coord_flip()

ggsave("city_rank_bias.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs", width=5, height=4)
```

# Create Segregation and Urban form percentiles
```{r}
zips$D3B_percentile = zips$D3B
zips <- mutate(zips, D3B_percentile = ntile(zips$D3B_percentile, 100))
zips$D2B_E8MIXA_percentile = zips$D2B_E8MIXA
zips <- mutate(zips, D2B_E8MIXA_percentile = ntile(zips$D2B_E8MIXA_percentile, 100))
zips$D1C8_ENT_percentile = zips$D1C8_ENT
zips <- mutate(zips, D1C8_ENT_percentile = ntile(zips$D1C8_ENT_percentile, 100))
zips$urban_score = (zips$D3B_percentile + zips$D2B_E8MIXA_percentile + zips$D1C8_ENT_percentile)/3
zips$segregation_percentile = zips$segregation
zips <- mutate(zips, segregation_percentile = ntile(zips$segregation_percentile, 100))
zips$bias_grp_mem_zip_percentile = zips$bias_grp_mem_zip
zips <- mutate(zips, bias_grp_mem_zip_percentile = ntile(zips$bias_grp_mem_zip_percentile, 100))
```

####### Seattle ####### 

```{r}
(cities[cities$cbsatitle == "Seattle",]$segregation - mean(cities$segregation))/sd(cities$segregation)
cities[cities$cbsatitle == "Seattle",]$segregation
mean(cities$segregation)

(cities[cities$cbsatitle == "Seattle",]$bias_grp_mem_zip - mean(cities$bias_grp_mem_zip))/sd(cities$bias_grp_mem_zip)
cities[cities$cbsatitle == "Seattle",]$bias_grp_mem_zip
mean(cities$bias_grp_mem_zip)

```


# Subset
```{r}
seattle <- subset(zips, cbsatitle == "Seattle-Tacoma-Bellevue, WA")

(seattle[seattle$zip == 98037,]$segregation - mean(seattle$segregation))/sd(seattle$segregation)
(seattle[seattle$zip == 98037,]$bias_grp_mem_zip - mean(seattle$bias_grp_mem_zip, na.rm=TRUE))/sd(seattle$bias_grp_mem_zip, na.rm=TRUE)

(seattle[seattle$zip == 98037,]$D3B - mean(seattle$D3B, na.rm=TRUE))/sd(seattle$D3B, na.rm=TRUE)
(seattle[seattle$zip == 98037,]$D2B_E8MIXA - mean(seattle$D2B_E8MIXA, na.rm=TRUE))/sd(seattle$D2B_E8MIXA, na.rm=TRUE)
(seattle[seattle$zip == 98037,]$D1C8_ENT - mean(seattle$D1C8_ENT, na.rm=TRUE))/sd(seattle$D1C8_ENT, na.rm=TRUE)
98404
```

```{r}
seattle <- subset(zips, cbsatitle == "Seattle-Tacoma-Bellevue, WA")

(seattle[seattle$zip == 98404,]$segregation - mean(seattle$segregation))/sd(seattle$segregation)
(seattle[seattle$zip == 98404,]$bias_grp_mem_zip - mean(seattle$bias_grp_mem_zip, na.rm=TRUE))/sd(seattle$bias_grp_mem_zip, na.rm=TRUE)

(seattle[seattle$zip == 98404,]$D3B - mean(seattle$D3B, na.rm=TRUE))/sd(seattle$D3B, na.rm=TRUE)
(seattle[seattle$zip == 98404,]$D2B_E8MIXA - mean(seattle$D2B_E8MIXA, na.rm=TRUE))/sd(seattle$D2B_E8MIXA, na.rm=TRUE)
(seattle[seattle$zip == 98404,]$D1C8_ENT - mean(seattle$D1C8_ENT, na.rm=TRUE))/sd(seattle$D1C8_ENT, na.rm=TRUE)

```

#Find Seattle zips
# Good Zip = 98037
```{r}
test <- subset(seattle, segregation < 0.2)
head(test)

seattle_good <- subset(seattle, zip == 98037)
mean(seattle$diversity, na.rm=TRUE)
seattle_good$D2B_E8MIXA
```

# Bad Zip = 98404
```{r}
sample <- subset(seattle, segregation > 0.5)
head(sample)

seattle_bad <- subset(seattle, zip == 98404)
mean(seattle$D1C8_ENT, na.rm=TRUE)
seattle_bad$D1C8_ENT

```

```{r}
ggplot(seattle, aes(x = segregation, y = bias_grp_mem_zip)) +
  geom_point(size=1) +
  geom_smooth(method='lm',formula=y~x) +
  geom_point(data = seattle_good, aes(x=segregation, y=bias_grp_mem_zip), color="green", size=4) +
  geom_text(data=seattle_good, aes(x=segregation, y=bias_grp_mem_zip), label="Lynnwood, WA (98037)", nudge_x = 0.03, nudge_y = -0.01) +
  geom_point(data = seattle_bad, aes(x=segregation, y=bias_grp_mem_zip), color="red", size=4) +
  geom_text(data=seattle_bad, aes(x=segregation, y=bias_grp_mem_zip), label="Tacoma, WA (98404)", nudge_x = 0.03, nudge_y = -0.01) +
  xlab("Experienced Economic Segregation") + 
  ylab("Friending Bias")

# ggsave("seattle_segregation_vs_friending_bias.pdf", path="/Users/georgecrowne/Desktop/Thesis/figs")

```

```{r}
seattle$urban_form = scale((scale(seattle$D3B) + scale(seattle$D1C8_ENT) + scale(seattle$D2B_E8MIXA))/3)
```


```{r}
ggplot(seattle, aes(x = urban_form, y = segregation)) +
  geom_point(size=1) +
  geom_smooth(method='lm',formula=y~x) +
  geom_point(data = seattle_good, aes(x=urban_form, y=segregation), color="green", size=4) +
  geom_text(data=seattle_good, aes(x=urban_form, y=segregation), label="Lynnwood, WA (98037)", nudge_x = 0.03, nudge_y = -0.01) +
  geom_point(data = seattle_bad, aes(x=urban_form, y=segregation), color="red", size=4) +
  geom_text(data=seattle_bad, aes(x=urban_form, y=segregation), label="Tacoma, WA (98404)", nudge_x = 0.03, nudge_y = -0.01) +
  xlab("Employment Entropy") + 
  ylab("Experienced Economic Segregation")

summary(lm(segregation ~ urban_form, data=seattle))

# ggsave("seattle_employment_entropy_vs_segregation.pdf", path="/Users/georgecrowne/Desktop/Thesis/figs")
```


####### NYC ####### 
# Subset
```{r}
nyc <- subset(zips, cbsatitle == "New York-Newark-Jersey City, NY-NJ-PA")
```
#Find nyc zips
# Good Zip = 10016
```{r}
test <- subset(nyc, segregation < 0.3)
test <- subset(test, bias_grp_mem_zip < 0)
head(test)

nyc_good <- subset(nyc, zip == 10016)
mean(nyc$D1C8_ENT, na.rm=TRUE)
nyc_good$D1C8_ENT
```

# Bad Zip = 11218
```{r}
sample <- subset(nyc, segregation > 0.65)
nyc_bad <- subset(sample, bias_grp_mem_zip > 0.35)
head(sample)

nyc_bad <- subset(nyc, zip == 11218)
mean(nyc$D1C8_ENT, na.rm=TRUE)
nyc_bad$D1C8_ENT

```

```{r}
ggplot(nyc, aes(x = segregation, y = bias_grp_mem_zip)) +
  geom_point(size=1, alpha=0.3) +
  # stat_summary_bin(fun.y = mean, bins=50,
  #                  color='black', size=2, geom='point', alpha=1) +
  geom_smooth(method='lm',formula=y~x) +
  geom_point(data = nyc_good, aes(x=segregation, y=bias_grp_mem_zip), color="green", size=4) +
  geom_text(data=nyc_good, aes(x=segregation, y=bias_grp_mem_zip), label="ZIP code 10016", nudge_x = 0.00, nudge_y = -0.03) +
  geom_point(data = nyc_bad, aes(x=segregation, y=bias_grp_mem_zip), color="red", size=4) +
  geom_text(data= nyc_bad, aes(x=segregation, y=bias_grp_mem_zip), label="ZIP code 11218", nudge_x = 0.03, nudge_y = 0.03) +
  xlab("Experienced Economic Segregation") + 
  ylab("Friending Bias")

ggsave("nyc_segregation_vs_friending_bias.pdf", path="/Users/georgecrowne/Desktop/Thesis/figs")

```

####### DETROIT ##############

# Subset for Detroit
```{r}
detroit <- subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
sf <- subset(zips, cbsatitle == "San Francisco-Oakland-Hayward, CA")
nyc = subset(zips, cbsatitle == "New York-Newark-Jersey City, NY-NJ-PA")
```

```{r}
(detroit[detroit$zip == 48226,]$segregation - mean(detroit$segregation))/sd(detroit$segregation)
mean(detroit$segregation)
```


# Get summary stats for Detroit and SF
```{r}
mean(detroit$D3B)
mean(detroit$D1C8_ENT)
mean(detroit$D2B_E8MIXA)
mean(detroit$segregation)

mean(sf$D3B)
mean(sf$D1C8_ENT)
mean(sf$D2B_E8MIXA)
mean(sf$segregation)

(mean(sf$D3B) - mean(detroit$D3B)) / mean(detroit$D3B)
(mean(sf$D1C8_ENT) - mean(detroit$D1C8_ENT)) / mean(detroit$D1C8_ENT)
(mean(sf$D2B_E8MIXA) - mean(detroit$D2B_E8MIXA)) / mean(detroit$D2B_E8MIXA)

(mean(sf$segregation) - mean(detroit$segregation)) / mean(detroit$segregation)
```

# Find bad zip code in Detroit - 48204
```{r}
detroit = subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
detroit$D3B_percentile = detroit$D3B
detroit <- mutate(detroit, D3B_percentile = ntile(detroit$D3B_percentile, 100))
detroit$D2B_E8MIXA_percentile = detroit$D2B_E8MIXA
detroit <- mutate(detroit, D2B_E8MIXA_percentile = ntile(detroit$D2B_E8MIXA_percentile, 100))
detroit$D1C8_ENT_percentile = detroit$D1C8_ENT
detroit <- mutate(detroit, D1C8_ENT_percentile = ntile(detroit$D1C8_ENT_percentile, 100))
detroit$urban_score = (detroit$D3B_percentile + detroit$D2B_E8MIXA_percentile + detroit$D1C8_ENT_percentile)/3
detroit$segregation_percentile = detroit$segregation
detroit <- mutate(detroit, segregation_percentile = ntile(detroit$segregation_percentile, 100))
```

```{r}
detroit_bad$segregation
mean(detroit$segregation)
```


```{r}
detroit_good <- subset(detroit, D3B == max(detroit$D3B))
```

```{r}
(detroit[detroit$zip == 48226,]$segregation - mean(detroit$segregation))/sd(detroit$segregation)
detroit_bad <- subset(detroit, zip == 48204)
(detroit_bad$bias_grp_mem_zip - mean(detroit$bias_grp_mem_zip, na.rm=TRUE))/sd(detroit$bias_grp_mem_zip, na.rm=TRUE)
(detroit_good$bias_grp_mem_zip - mean(detroit$bias_grp_mem_zip, na.rm=TRUE))/sd(detroit$bias_grp_mem_zip, na.rm=TRUE)

```


```{r}
detroit = subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
detroit_good <- subset(detroit, D3B == max(detroit$D3B))

ggplot() +
  geom_point(data = detroit, aes(x = D2B_E8MIXA, y = segregation), color="blue") +
  geom_smooth(data = detroit, aes(x = D2B_E8MIXA, y=segregation), method="lm", formula = y~x)+
  geom_point(data = detroit_bad, aes(x=D2B_E8MIXA, y=segregation), color="red", size=4) +
  geom_text(data=detroit_bad, aes(x=D2B_E8MIXA, y=segregation), label="Nardin Park (48204)", nudge_x = 0.04, nudge_y = 0.04) +
  geom_point(data = detroit_good, aes(x=D2B_E8MIXA, y=segregation), color="dark green", size=4) +
  geom_text(data= detroit_good, aes(x=D2B_E8MIXA, y=segregation), label="Downtown Core (48226)", nudge_x = 0.01, nudge_y = -0.04) +
  xlab("Employment Entropy") +
  ylab("Experienced Economic Segregation")

# ggsave("detroit_employment_entropy_vs_segregation.pdf", path="/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
detroit = subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
detroit_bad <- subset(detroit, zip == 48204)
detroit_good <- subset(detroit, D3B == max(detroit$D3B))

ggplot() +
  geom_point(data = detroit, aes(x = segregation, y = bias_grp_mem_zip), color="blue") +
  geom_smooth(data = detroit, aes(x = segregation, y=bias_grp_mem_zip), method="lm", formula = y~x)+
  geom_point(data = detroit_bad, aes(x=segregation, y=bias_grp_mem_zip), color="red", size=4) +
  geom_text(data=detroit_bad, aes(x=segregation, y=bias_grp_mem_zip), label="Nardin Park \n(48204)", nudge_x = 0.045, nudge_y = 0.01) +
  geom_point(data = detroit_good, aes(x=segregation, y=bias_grp_mem_zip), color="dark green", size=4) +
  geom_text(data= detroit_good, aes(x=segregation, y=bias_grp_mem_zip), label="Downtown Core (48226)", nudge_x = 0.04, nudge_y = -0.02) +
  xlab("Experienced Economic Segregation") +
  ylab("Friending Bias")

ggsave("detroit_segregation_vs_bias.pdf", path="/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
detroit = subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
detroit_bad <- subset(detroit, zip == 48204)

ggplot() +
  geom_point(data = detroit, aes(x = log(D1C8_ENT), y = segregation), color="blue") +
  geom_smooth(data = detroit, aes(x = log(D1C8_ENT), y=segregation), method="lm", formula = y~x)+
  geom_point(data = detroit_bad, aes(x=log(D1C8_ENT), y=segregation), color="red", size=4) +
  geom_text(data=detroit_bad, aes(x=log(D1C8_ENT), y=segregation), label="Nardin Park (48204)", nudge_x = 0.04, nudge_y = 0.04) +
  geom_point(data = detroit_good, aes(x=log(D1C8_ENT), y=segregation), color="dark green", size=4) +
  geom_text(data= detroit_good, aes(x=log(D1C8_ENT), y=segregation), label="Downtown Core (48226)", nudge_x = 0.01, nudge_y = -0.04) +
  xlab("Log[Entertainment Place Density]") +
  ylab("Experienced Economic Segregation")
```

```{r}
zips$D3B
detroit = subset(zips, cbsatitle == "Detroit-Warren-Dearborn, MI")
detroit_bad <- subset(detroit, zip == 48204)

ggplot() +
  geom_point(data = detroit, aes(x = D3B, y = segregation), color="blue") +
  geom_smooth(data = detroit, aes(x = D3B, y=segregation), method="lm", formula = y~x)+
  geom_point(data = detroit_bad, aes(x=D3B, y=segregation), color="red", size=4) +
  geom_text(data=detroit_bad, aes(x=D3B, y=segregation), label="Nardin Park (48204)", nudge_x = 0.04, nudge_y = 0.04) +
  geom_point(data = detroit_good, aes(x=D3B, y=segregation), color="dark green", size=4) +
  geom_text(data= detroit_good, aes(x=D3B, y=segregation), label="Downtown Core (48226)", nudge_x = 0.01, nudge_y = -0.04) +
  xlab("Log[Entertainment Place Density]") +
  ylab("Experienced Economic Segregation")
```


```{r}
ggplot(detroit, aes(x = segregation, y = urban_score)) +
  geom_point(size=1) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Segregation") + 
  ylab("Urban Form")

summary(lm(urban_score ~ segregation, data=detroit))

# ggsave("cuebiq_cities_ec.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
zips$D1C8_ENT
ggplot(sf, aes(x = segregation, y = D1C8_ENT)) +
  geom_point(size=1) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Segregation") + 
  ylab("Urban Form")

summary(lm(urban_score ~ segregation, data=sf))

# ggsave("cuebiq_cities_ec.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
ggplot() +
  geom_point(data = sf, aes(x = segregation, y = urban_score), color = "blue") + # must include argument label "data"
  geom_point(data = detroit, aes(x = segregation, y = urban_score), color="red")
```


```{r}
mean(detroit$segregation)
mean(sf$segregation)

mean(detroit$urban_score)
mean(sf$urban_score)

ggplot() +
  geom_point(data = detroit, aes(x = urban_score, y = segregation), color="blue") +
  geom_smooth(data = detroit, aes(x = urban_score, y=segregation), method="lm", formula = y~x) +
  geom_point(data = sf, aes(x = urban_score, y = segregation), color="red") +
  geom_smooth(data = sf, aes(x = urban_score, y=segregation), method="lm", formula = y~x, color = 'red')
```


# Find good zip code in SF - 94111
```{r}
sf = subset(zips, cbsatitle == "San Francisco-Oakland-Hayward, CA")
sf[which.min(sf$segregation),]
sf$D3B_percentile = sf$D3B
sf <- mutate(sf, D3B_percentile = ntile(sf$D3B_percentile, 100))
sf$D2B_E8MIXA_percentile = sf$D2B_E8MIXA
sf <- mutate(sf, D2B_E8MIXA_percentile = ntile(sf$D2B_E8MIXA_percentile, 100))
sf$D1C8_ENT_percentile = sf$D1C8_ENT
sf <- mutate(sf, D1C8_ENT_percentile = ntile(sf$D1C8_ENT_percentile, 100))
sf$urban_score = (sf$D3B_percentile + sf$D2B_E8MIXA_percentile + sf$D1C8_ENT_percentile)/3
sf$segregation_percentile = sf$segregation
sf <- mutate(sf, segregation_percentile = ntile(sf$segregation_percentile, 100))
```
```{r}
sf_good <- subset(sf, zip == 94111)
sf_good$segregation
sf_good$D3B
sf_good$D1C8_ENT
sf_good$D2B_E8MIXA
```



####### Seattle VS NYC ##############

# Subset for seattle and nyc
```{r}
nyc = subset(zips, cbsatitle == "New York-Newark-Jersey City, NY-NJ-PA")
seattle = subset(zips, cbsatitle == "Seattle-Tacoma-Bellevue, WA")
```

# Plot segregation and friending bias in both cities
```{r}
ggplot() +
  geom_point(data = nyc, aes(x = segregation_percentile, y = bias_grp_mem_zip), color="blue") +
  geom_smooth(data = nyc, aes(x = segregation_percentile, y=bias_grp_mem_zip), method="lm", formula = y~x) +
  geom_point(data = seattle, aes(x = segregation_percentile, y = bias_grp_mem_zip), color="red") +
  geom_smooth(data = seattle, aes(x = segregation_percentile, y=bias_grp_mem_zip), method="lm", formula = y~x, color = 'red')
```

# Plot segregation and friending bias in Seattle

```{r}

```


# Bad NYC zip - 10455
```{r}
test <- subset(nyc, zip == 10455)
head(test$segregation_percentile)
head(test$bias_grp_mem_zip_percentile)
```

# Good NYC zip - 10128
```{r}
test <- subset(nyc, zip == 10128)
head(test$segregation_percentile)
head(test$bias_grp_mem_zip_percentile)
```

# Seattle Good 
```{r}
test <- subset(seattle, segregation_percentile < 5)
test <- subset(seattle, zip == 98026)
head(test$segregation_percentile)
head(test$bias_grp_mem_zip_percentile)
head(test$population_density)
```

# NYC And Seattle Means
```{r}
mean(nyc$segregation)
mean(seattle$segregation)
(mean(nyc$segregation) - mean(seattle$segregation))/mean(seattle$segregation)

mean(nyc$bias_grp_mem_zip, na.rm=TRUE)
mean(seattle$bias_grp_mem_zip, na.rm=TRUE)
(mean(nyc$bias_grp_mem_zip, na.rm=TRUE) - mean(seattle$bias_grp_mem_zip, na.rm=TRUE))/mean(seattle$bias_grp_mem_zip, na.rm=TRUE)
```



# Map zip codes
```{r}
head(zips)
```




















# Group cuebiq data by city
```{r}
cols = cuebiq_data %>% select(
  city_name,
  pcat,
  nusers,
  nstays,
  segregation,
  p1a,
  p2a,
  p3a,
  p4a,
)

cities <- cols %>%
  group_by(city_name) %>%
  summarize_at(vars(segregation:p4a),funs(weighted.mean(., w=nstays)))
```

# Get counties in cuebiq CBSAs
```{r}
cbsas <- c(
  "New York-Newark-Jersey City, NY-NJ-PA",
  "Los Angeles-Long Beach-Anaheim, CA",
  "Chicago-Naperville-Elgin, IL-IN-WI",
  "Dallas-Fort Worth-Arlington, TX",
  "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD",
  "Washington-Arlington-Alexandria, DC-VA-MD-WV",
  "Miami-Fort Lauderdale-West Palm Beach, FL",
  "Boston-Cambridge-Newton, MA-NH",
  "San Francisco-Oakland-Hayward, CA",
  "Detroit-Warren-Dearborn, MI",
  "Seattle-Tacoma-Bellevue, WA"
)

counties <- subset(cbsa, cbsatitle %in% cbsas)
counties = rename(counties, "state_fips" = "fipsstatecode")
counties = rename(counties, "county_fips" = "fipscountycode")
data = rename(data, "state_fips"= "Geo_STATE")
data = rename(data, "county_fips" = "county")

counties <- counties %>%
  left_join(data, by = c("county_fips", "state_fips"))
```

# See the counties
```{r}
df <- data.frame(
    fips = counties$county_code,
    values = counties$urban
)

plot_usmap(data = df, color = "NA")

ggsave("cuebiq_counties.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs/maps")
```

# Aggregate over the cities
```{r}
cols = counties %>% select(
  cbsatitle,
  pop2018,
  ec_county,
  exposure_grp_mem_county,
  bias_grp_mem_county
)

cities_ec <- cols %>%
  group_by(cbsatitle) %>%
  summarize_at(vars(ec_county:bias_grp_mem_county),funs(weighted.mean(., w=pop2018, na.rm=TRUE)))

cities_ec[cities_ec$cbsatitle == "Boston-Cambridge-Newton, MA-NH",]$cbsatitle = "Boston"
cities_ec[cities_ec$cbsatitle == "Chicago-Naperville-Elgin, IL-IN-WI",]$cbsatitle = "Chicago"
cities_ec[cities_ec$cbsatitle == "Dallas-Fort Worth-Arlington, TX",]$cbsatitle = "Dallas"
cities_ec[cities_ec$cbsatitle == "Detroit-Warren-Dearborn, MI",]$cbsatitle = "Detroit"
cities_ec[cities_ec$cbsatitle == "Los Angeles-Long Beach-Anaheim, CA",]$cbsatitle = "Los Angeles"
cities_ec[cities_ec$cbsatitle == "Miami-Fort Lauderdale-West Palm Beach, FL",]$cbsatitle = "Miami"
cities_ec[cities_ec$cbsatitle == "New York-Newark-Jersey City, NY-NJ-PA",]$cbsatitle = "New York City"
cities_ec[cities_ec$cbsatitle == "Philadelphia-Camden-Wilmington, PA-NJ-DE-MD",]$cbsatitle = "Philadelphia"
cities_ec[cities_ec$cbsatitle == "Seattle-Tacoma-Bellevue, WA",]$cbsatitle = "Seattle"
cities_ec[cities_ec$cbsatitle == "San Francisco-Oakland-Hayward, CA",]$cbsatitle = "San Francisco"
cities_ec[cities_ec$cbsatitle == "Washington-Arlington-Alexandria, DC-VA-MD-WV",]$cbsatitle = "Washington"

cities_ec <- rename(cities_ec, "city_name" = "cbsatitle")

cities <- cities %>% 
  left_join(cities_ec, by = c("city_name"))
```

```{r}
ggplot(cities, aes(x = segregation, y = bias_grp_mem_zip)) +
  geom_point(color="magenta", size=3) +
  geom_label_repel(aes(label = cbsatitle),
                    fill="darkblue", color = 'white',
                    size = 4) +
  xlab("Segregation") + 
  ylab("Economic Connectedness")

# ggsave("cuebiq_cities_ec.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
ggplot(cities, aes(x = segregation, y = bias_grp_mem_county)) +
  geom_point(color="magenta", size=3) +
  geom_label_repel(aes(label = city_name),
                    fill="darkblue", color = 'white',
                    size = 4) +
  xlab("Segregation") + 
  ylab("Friending Bias")

ggsave("cuebiq_cities_fb.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
library(ggplot2)
library(scales)
theme_set(theme_classic())


# prep data
left_label <- cities$cbsatitle
right_label <- cities$cbsatitle

cities$segregation_percentile = cities$segregation
cities <- mutate(cities, segregation_percentile = ntile(cities$segregation_percentile, 100))

cities$bias_grp_mem_zip_percentile = cities$bias_grp_mem_zip
cities <- mutate(cities, bias_grp_mem_zip_percentile = ntile(cities$bias_grp_mem_zip_percentile, 100))

cities$flag <- ifelse(abs(cities$bias_grp_mem_zip_percentile - cities$segregation_percentile) > 20, "red", "green")


# Plot
p <- ggplot(cities) + geom_segment(aes(x=1, xend=2, y=segregation_percentile, yend=bias_grp_mem_zip_percentile, col=flag), size=.75, show.legend=F) + 
                  geom_vline(xintercept=1, linetype="dashed", size=.1) + 
                  geom_vline(xintercept=2, linetype="dashed", size=.1) +
                  scale_color_manual(labels = c("Up", "Down"), 
                                     values = c("green"="#00ba38", "red"="#f8766d")) +  # color of lines
                  labs(x="", y="Mean GdpPerCap") +  # Axis labels
                  xlim(.5, 2.5) + ylim(0,(1.1*(max(cities$bias_grp_mem_zip_percentile, cities$segregation_percentile))))  # X and Y axis limits

# Add texts

p <- p + geom_text(label= left_label, y=cities$segregation_percentile, x=rep(1, NROW(cities)), hjust=1.1, size=3.5)
p <- p + geom_text(label= right_label, y=cities$bias_grp_mem_zip_percentile, x=rep(2, NROW(cities)), hjust=-0.1, size=3.5)
p <- p + geom_text(label="Segregation", x=1, y=1.1*(max(cities$segregation_percentile, cities$bias_grp_mem_zip_percentile)), hjust=1.2, size=5)  # title
p <- p + geom_text(label="Bias", x=2, y=1.1*(max(cities$segregation_percentile, cities$bias_grp_mem_zip_percentile)), hjust=-0.1, size=5)  # title

# Minify theme
p + theme(panel.background = element_blank(), 
           panel.grid = element_blank(),
           axis.ticks = element_blank(),
           axis.text.x = element_blank(),
           panel.border = element_blank(),
           plot.margin = unit(c(1,2,1,2), "cm"))
```

```{r}
library(ggmap)
library(maps)
library(maptools)
zip_shape <- readShapePoly("Data/raw/cb_2018_us_zcta510_500k.shp")

merged_data <- merge(shapefile@data, zips, by.x = "ZCTA5CE10", by.y ="zip")

merged_data$Geo_INTPTLAT

ggplot() +
  geom_polygon(data = merged_data, aes(x = Geo_INTPTLON, y = Geo_INTPTLAT, fill = segregation)) +
  coord_equal() +
  ggtitle("Zip Code Level Data") +
  scale_fill_gradient(low = "white", high = "red", na.value = "gray80") +
  theme_void()
```

```{r}
library(dplyr)
library(ggplot2)
library(stringr)
library(rgdal) 
library(maptools)
library(rgdal)
library(rgeos)

shapefile <- readShapePoly("Data/raw/cb_2018_us_zcta510_500k.shp")

zips$zip = as.character(zips$zip)

zips %>% 
  mutate(zip = str_pad(zip, 5, side="left", "0"))

states <- map_data("state")

uspoly <- subset(shapefile, ZCTA5CE10 %in% zips$zip)

uspoly$group <- substr(uspoly$ZCTA5CE10, 1,3)

uspoly$ZCTA5CE10 <- droplevels(uspoly$ZCTA5CE10)

uspoly.union <- unionSpatialPolygons(uspoly, uspoly$group)

uspolyfort_A <- fortify(uspoly.union)

usmap_A <- uspolyfort_A %>%
  select(long, lat, order, group) %>%
  mutate(Territory_A = "In") %>%
  mutate(group = as.numeric(group)) %>%
  bind_rows(states %>%
              select(long, lat, order, group) %>%
              mutate(Territory_A = "Out") %>%
              mutate(group = group + max(as.numeric(uspolyfort_A$group))))

ggplot(usmap_A) +
  geom_polygon(aes(x = long, y = lat, group = group, fill = Territory_A, color = Territory_A)) + 
  scale_colour_manual(aesthetics = "fill", values=c("cornflowerblue", NA)) +
  scale_colour_manual(aesthetics = "color", values=c("cornflowerblue", "black")) + #Draws borders. (Zip border is the same as fill color for a cleaner look)
  coord_fixed(1.3) + 
  guides(fill=FALSE) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank(), axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(hjust = .5), legend.position ="none")  + 
  labs(title = "Territory A")
```



