---
title: "Urban Design vs Social Capital ZIP CODE LEVEL"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(jtools)
library(stargazer)
library(datawizard)
library(plm)
library(lfe)
pacman::p_load(tidyverse, estimatr, ggplot2, dplyr, jtools, ggstance, broom.mixed, fabricatr) # You should install these packages.

rm(list = ls())
setwd("~/Desktop/Thesis")
data <- read.csv("Data/working/data_merged_zip.csv")
cuebiq <- read.csv("Data/working/cuebiq_zip.csv")
```

# Create Figure
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          scale(median_household_income) +  
          scale(population_density) +
          scale(D3B) +
          scale(D2B_E8MIXA) +
          scale(D1C8_ENT),
          data = data)
  return(model)
}

plot_summs(estimate_horserace_regression(data$bias_grp_mem_zip), estimate_horserace_regression(data$ec_zip),
           estimate_horserace_regression(data$exposure_grp_mem_zip),

           coefs = c(
                     "Household Income" = "scale(median_household_income)",
                     "Population Density" = "scale(population_density)",
                     "Street Intersection Density" = "scale(D3B)",
                     "Employment Entropy" = "scale(D2B_E8MIXA)",
                     "Entertainment Place Density" = "scale(D1C8_ENT)"
                     ),

           robust = list("HC0","HC0", "HC0"),
           model.names =c("Friending Bias", "Economic Connectedness", "Exposure"))

# ggsave("features_density_horse_race.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

# Create Summary Table
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          log(median_household_income) + 
          log(population_density) +
          D3B +
          D2B_E8MIXA +
          D1C8_ENT,
          data = data)
  return(model)
}

lm1 <- estimate_horserace_regression(data$ec_zip)
lm2 <- estimate_horserace_regression(data$bias_grp_mem_zip)
lm3 <- estimate_horserace_regression(data$exposure_grp_mem_zip)

mean_ec <- round(mean(data$ec_zip, na.rm = TRUE), 3)
mean_bias <- round(mean(data$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_exp <- round(mean(data$exposure_grp_mem_zip, na.rm = TRUE), 3)

sd_ec <- round(sd(data$ec_zip, na.rm=TRUE), 3)
sd_bias <- round(sd(data$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_exp <- round(sd(data$exposure_grp_mem_zip, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, 
          title="Urban Design vs Social Capital",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Household Income",
            "Population Density",
            "Street Intersection Density",
            "Employment Entropy",
            "Entertainment Place Density"
            ),
          add.lines = list(c("Mean", mean_ec, mean_bias, mean_exp), c("Std. Dev", sd_ec, sd_bias, sd_exp)),
          table.placement="p"
          )

# write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/table8.txt")
```

# Get Experienced Segregation and number of visits for each zip
```{r}
cuebiq$bias <- ((cuebiq$p1a + cuebiq$p2a) - (cuebiq$p3a + cuebiq$p4a))^2

cols = cuebiq %>% select(
  postcode,
  nstays,
  segregation,
  bias
)

zips <- cols %>% 
  group_by(postcode) %>% 
  summarize(across(c(segregation, bias),function (x) weighted.mean(x, w=nstays, na.rm=TRUE)))

zips_nstays <- cols %>% 
  group_by(postcode) %>% 
  summarize_at(vars(nstays), funs(mean))

# Accounts for DC/Maryland & Virginia issue
# data[data$state_fips == 24,]$state_fips = 11
# data[data$state_fips == 51,]$state_fips = 11

zips <- rename(zips, "zip" = "postcode")
zips$zip = as.integer(zips$zip)
zips_nstays <- rename(zips_nstays, "zip" = "postcode")
zips_nstays$zip = as.integer(zips_nstays$zip)

zips <- zips %>%
  inner_join(data, by = c("zip"))

zips_nstays <- zips_nstays %>%
  left_join(data, by = c("zip"))
```

```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          scale(median_household_income) +  
          scale(population_density) +
          scale(D3B) +
          scale(D2B_E8MIXA) +
          scale(D1C8_ENT),
          data = zips)
  return(model)
}

plot_summs(estimate_horserace_regression(zips$segregation),
           estimate_horserace_regression(zips$segregation),

           coefs = c(
                     "Household Income" = "scale(median_household_income)",
                     "Population Density" = "scale(population_density)",
                     "Street Intersection Density" = "scale(D3B)",
                     "Employment Entropy" = "scale(D2B_E8MIXA)",
                     "Entertainment Place Density" = "scale(D1C8_ENT)"
                     ),

           robust = list("HC0", "HC0"),
           model.names = ("Experienced Income Segregation"),
           legend.title = "Model")

ggsave("zip_urban_form_vs_segregation.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          scale(median_household_income) +  
          scale(population_density) +
          scale(segregation),
          data = zips)
  return(model)
}

plot_summs(estimate_horserace_regression(zips$bias_grp_mem_zip),
           estimate_horserace_regression(zips$bias_grp_mem_zip),

           coefs = c(
                     "Household Income" = "scale(median_household_income)",
                     "Population Density" = "scale(population_density)",
                     "Experienced Income Segregation" = "scale(segregation)"
                     ),

           robust = list("HC0", "HC0"),
           model.names = ("Friending Bias"),
           legend.title = "Model")

ggsave("zip_segregation_vs_friending_bias.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```


# Don't worry about this
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(scale(outcome) ~
          scale(log(Median_Household_Income_2020)) + 
          scale(log(popdensity2010)) +
          scale(D3B) +
          scale(D2B_E8MIXA) +
          scale(NatWalkInd),
          data = counties)
  return(model)
}

plot_summs(estimate_horserace_regression(counties$bias_grp_mem_county), estimate_horserace_regression(counties$ec_county),
           estimate_horserace_regression(counties$exposure_grp_mem_county),

           coefs = c("Household Income" = "scale(log(Median_Household_Income_2020))",
                     "Population Density" = "scale(log(popdensity2010))",
                     "Street Intersection Density" = "scale(D3B)",
                     "Employment Entropy" = "scale(D2B_E8MIXA)",
                     "Walkability Index" = "scale(NatWalkInd)"
                     ),

           robust = list("HC0","HC0", "HC0"),
           model.names =c("Friending Bias", "Economic Connectedness", "Exposure"))
```

#Standardize all variables
```{r}
zips$segregation = scale(zips$segregation)
zips$bias_grp_mem_zip = scale(zips$bias_grp_mem_zip)
zips$D3B = scale(zips$D3B)
zips$D2B_E8MIXA = scale(zips$D2B_E8MIXA)
zips$D1C8_ENT = scale(zips$D1C8_ENT)
zips$population_density = scale(zips$population_density)
zips$pop2018 = scale(zips$pop2018)
zips$median_household_income = scale(zips$median_household_income)
zips$diversity = scale(zips$diversity)
zips$college_rates = scale(zips$college_rates)
zips$unemployment_rate = scale(zips$unemployment_rate)

zips$D1C8_ED = scale(zips$D1C8_ED)
zips$D1C8_HLTH = scale(zips$D1C8_HLTH)
zips$D1C8_IND = scale(zips$D1C8_IND)
zips$D1C8_OFF = scale(zips$D1C8_OFF)
zips$D1C8_RET = scale(zips$D1C8_RET)
zips$D1C8_SVC = scale(zips$D1C8_SVC)
zips$D1C8_PUB = scale(zips$D1C8_PUB)

zips$intersect_density_km = scale(zips$intersect_density_km)
```

```{r}
model <- lm(segregation ~ D1C8_ENT, data=zips)
model2 <- lm(segregation ~ D1C8_ED, data=zips)
model3<- lm(segregation ~ D1C8_IND, data=zips)
model4 <- lm(segregation ~ D1C8_OFF, data=zips)
model5 <- lm(segregation ~ D1C8_RET, data=zips)
model6 <- lm(segregation ~ D1C8_SVC, data=zips)
model7 <- lm(segregation ~ D1C8_PUB, data=zips)
model8 <- lm(segregation ~ D1C8_HLTH, data=zips)

plot_summs(model, model2, model3, model4, model5, model6, model7, model8, colors="Rainbow")
```

```{r}
library(coefplot)

model1 <- lm(segregation ~ D1C8_ENT, data = zips)
model2 <- lm(segregation ~ D1C8_ED, data = zips)
model3 <- lm(segregation ~ D1C8_PUB, data = zips)

coefplot(list(model1, model2, model3))
```


# Plot segregation against employment entropy
```{r}
res1 <- resid(lm(D2B_E8MIXA ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
res2 <- resid(lm(segregation ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))

summary(lm(segregation ~ D2B_E8MIXA + population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
summary(lm(res2 ~ res1))

df <- data.frame(res1, res2)

ggplot(df,aes(x=res1,y=res2)) + 
  # geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  xlab("Employment Entropy") + 
  ylab("Experienced Economic Segrgation")  

# ggsave("zip_employment_entropy_vs_segregation.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
lm1 <- lm(segregation ~ D2B_E8MIXA, data=zips)
lm2 <- lm(segregation ~ D2B_E8MIXA + population_density + median_household_income, data=zips)
lm3 <- lm(segregation ~ D2B_E8MIXA + 
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(segregation ~
            D2B_E8MIXA +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

# mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

# sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Employment Entropy vs Experienced Economic Segregation",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Employment Entropy",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_seg, mean_seg, mean_seg, mean_seg),
                            c("Std. Dev", sd_seg, sd_seg, sd_seg, sd_seg),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("City Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )

write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/employment_entropy_vs_segregation.txt")
```

# Plot segregation against intersection density
```{r}
res1 <- resid(lm(D3B ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
res2 <- resid(lm(segregation ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))

summary(lm(segregation ~ D3B + population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
summary(lm(res2 ~ res1))

df <- data.frame(res1, res2)

ggplot(df,aes(x=res1,y=res2)) + 
  # geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  xlab("Street Inersection Density") + 
  ylab("Experienced Economic Segrgation")  

# ggsave("zip_intersection_density_vs_segregation.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
lm1 <- lm(segregation ~ D3B, data=zips)
lm2 <- lm(segregation ~ D3B + population_density + median_household_income, data=zips)
lm3 <- lm(segregation ~ D3B + 
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(segregation ~
            D3B +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

# mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

# sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Intersection Density vs Experienced Economic Segregation",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Intersection Density",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_seg, mean_seg, mean_seg, mean_seg),
                            c("Std. Dev", sd_seg, sd_seg, sd_seg, sd_seg),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("County Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )

# write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/intersection_density_vs_segregation.txt")
```

```{r}
quantile(zips$D3B, 0.06)
test <- subset(zips, D3B < -1.315521 )
table(test$cbsatitle)
```

```{r}
hs <- subset(zips, zip==02138)
head(hs$bias_grp_mem_zip)
test <- subset(zips,Geo_STATE==25 & bias_grp_mem_zip > -1.131981 + 0.07 & bias_grp_mem_zip < -1.131981 + 0.09)
head(test)
ec <- subset(zips, zip == 02141)
head(ec$bias_grp_mem_zip)
```



```{r}
summary(lm(segregation ~ D3B + population_density + median_household_income + pop2018 + unemployment_rate + diversity, data=zips))
summary(lm(segregation ~ intersect_density_km + population_density + median_household_income + pop2018 + unemployment_rate + diversity, data=zips))
summary(felm(segregation~population_density + median_household_income + pop2018 + unemployment_rate + diversity | 0 | (D3B ~ intersect_density_km), data=zips))
```


```{r}
lm1 <- lm(segregation ~ intersect_density_km, data=zips)
lm2 <- lm(segregation ~ intersect_density_km + population_density + median_household_income, data=zips)
lm3 <- lm(segregation ~ intersect_density_km + 
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(segregation ~
            intersect_density_km +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

# mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

# sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Intersection Density vs Experienced Economic Segregation",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Intersection Density",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_seg, mean_seg, mean_seg, mean_seg),
                            c("Std. Dev", sd_seg, sd_seg, sd_seg, sd_seg),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("County Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )
```


# Plot segregation against entertainment place density
```{r}
res1 <- resid(lm(D1C8_ENT ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
res2 <- resid(lm(segregation ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))

summary(lm(segregation ~ D1C8_ENT + population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
summary(lm(res2 ~ res1))

df <- data.frame(res1, res2)

ggplot(df,aes(x=res1,y=res2)) + 
  # geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  xlab("Entertainment Place Density") + 
  ylab("Experienced Economic Segrgation")  

ggsave("zip_entertainment_density_vs_segregation.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
lm1 <- lm(segregation ~ D1C8_ENT, data=zips)
lm2 <- lm(segregation ~ D1C8_ENT + population_density + median_household_income, data=zips)
lm3 <- lm(segregation ~ D1C8_ENT + 
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(segregation ~
            D1C8_ENT +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

# mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

# sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Entertainment Place Density vs Experienced Economic Segregation",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Entertainment Place Density",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "College Rates",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_seg, mean_seg, mean_seg, mean_seg),
                            c("Std. Dev", sd_seg, sd_seg, sd_seg, sd_seg),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("City Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )

write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/entertainment_density_vs_segregation.txt")
```


# Determine magnitudes of changes
```{r}
test1 <- subset(zips, D1C8_ENT < 0.02 & D1C8_ENT > -0.02 & State.Abr. == "MA")
test2 <- subset(zips, D1C8_ENT < 1.03 & D1C8_ENT > 0.97 & State.Abr. == "MA")
test3 <- subset(zips, D1C8_ENT < 2.2 & D1C8_ENT > 1.8 & State.Abr. == "MA")
test4 <- subset(zips, D1C8_ENT < 3.1 & D1C8_ENT > 2.9 & State.Abr. == "MA")
# 02139

hs <- subset(zips, zip == 2116)
head(hs)
0.4100111 - 1
test <- subset(zips, D2B_E8MIXA > -0.6 & D2B_E8MIXA < -0.55  & State.Abr. == "MA")

```


# Create figure of urban form effects on segregation
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          median_household_income +  
          population_density +
            pop2018 +
            diversity +
            unemployment_rate +
          D3B +
          D1C8_ENT +
          D2B_E8MIXA,
          data = zips)
  return(model)
}

plot_summs(estimate_horserace_regression(zips$segregation),
           coefs = c(
                     "Street Intersection Density" = "D3B",
                     "Entertainment Place Density" = "D1C8_ENT",
                     "Employment Entropy" = "D2B_E8MIXA"
                     ),
           robust = c("HC0"),
           legend.title = "Outcome",
           model.names ="Experienced Economic Segregation")

ggsave("features_density_horse_race.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")  

```

# Create table
```{r}
lm1 <- lm(segregation ~ D3B + D1C8_ENT + D2B_E8MIXA , data=zips)
lm2 <- lm(segregation ~ D3B + D1C8_ENT + D2B_E8MIXA + population_density + median_household_income, data=zips)
lm3 <- lm(segregation ~ D3B + D1C8_ENT + D2B_E8MIXA +
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(segregation ~
            D3B + D1C8_ENT + D2B_E8MIXA  +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

# mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

# sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Urban Form vs Experienced Economic Segregation",
          covariate.labels=c(
            "Street Intersection Density",
            "Entertainment Place Density",
            "Employment Entropy",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_seg, mean_seg, mean_seg, mean_seg),
                            c("Std. Dev", sd_seg, sd_seg, sd_seg, sd_seg),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("City Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )

write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/urban_form_vs_segregation.txt")
```



# experienced Segregation vs Friending bias
```{r}
zips = subset(zips, !is.na(bias_grp_mem_zip))
res1 <- resid(lm(segregation ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
res2 <- resid(lm(bias_grp_mem_zip ~ population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))

summary(lm(bias_grp_mem_zip ~ segregation + population_density + median_household_income + pop2018 + diversity + unemployment_rate, data=zips))
summary(lm(res2 ~ res1))

df <- data.frame(res1, res2)

ggplot(df,aes(x=res1,y=res2)) + 
  # geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  xlab("Experienced Economic Segrgation") + 
  ylab("Friending Bias")  

ggsave("zip_segregation_vs_friending_bias.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

```{r}
lm1 <- lm(bias_grp_mem_zip ~ segregation, data=zips)
lm2 <- lm(bias_grp_mem_zip ~ segregation + population_density + median_household_income, data=zips)
lm3 <- lm(bias_grp_mem_zip ~ segregation + 
            population_density + 
            median_household_income +
            pop2018 +
            diversity +
            unemployment_rate, 
            data=zips)
lm4 <- lm(bias_grp_mem_zip ~
            segregation +
            median_household_income + 
            population_density + 
            pop2018 +
            diversity +
            unemployment_rate +
            as.factor(CBSA.title),
            data = zips)

mean_bias <- round(mean(zips$bias_grp_mem_zip, na.rm = TRUE), 3)
# mean_seg <- round(mean(zips$segregation, na.rm = TRUE), 3)

sd_bias <- round(sd(zips$bias_grp_mem_zip, na.rm=TRUE), 3)
# sd_seg <- round(sd(zips$segregation, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3, lm4, 
          title="Experienced Economic Segregation vs Friending Bias",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Experienced Economic Segregation",
            "Population Density",
            "Median Household Income",
            "Population",
            "Racial Diversity",
            "Unemployment Rates"
            ),
          add.lines = list(c("Mean", mean_bias, mean_bias, mean_bias, mean_bias),
                            c("Std. Dev", sd_bias, sd_bias, sd_bias, sd_bias),
                            c("Simple Controls", "No", "Yes", "Yes", "Yes"),
                            c("Full Controls", "No", "No", "Yes", "Yes"),
                            c("City Fixed Effects", "No", "No", "No", "Yes")),
          table.placement="H"
          )

write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/segregation_vs_friending_bias.txt")
```




# Correlate intersection density with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(zips$segregation ~ scale(zips$D3B))
lm2 <- lm(zips$segregation ~ scale(zips$D3B) + scale(zips$median_household_income))
lm3 <- lm(zips$segregation ~ scale(zips$D3B) + scale(zips$population_density))
lm4 <- lm(zips$segregation ~ scale(zips$D3B) + scale(zips$median_household_income) + scale(zips$population_density))
lm5 <- lm(zips$segregation ~
            scale(zips$D3B) +
            scale(zips$median_household_income) + 
            scale(zips$population_density) + 
            scale(zips$total_population_2) +
            scale(zips$diversity) +
            scale(zips$college_rates) +
            scale(zips$unemployment_rate),
            data = zips)

lm6 <- plm(segregation ~
            D3B +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate,
            data = zips,
            index = c("county"))

table <- stargazer(lm1, lm2, lm3, lm4, lm5, lm6)
```

# Correlate Employment Entropy with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(zips$segregation ~ scale(zips$D2B_E8MIXA))
lm2 <- lm(zips$segregation ~ scale(zips$D2B_E8MIXA) + scale(zips$median_household_income))
lm3 <- lm(zips$segregation ~ scale(zips$D2B_E8MIXA) + scale(zips$population_density))
lm4 <- lm(zips$segregation ~ scale(zips$D2B_E8MIXA) + scale(zips$median_household_income) + scale(zips$population_density))
lm5 <- lm(zips$segregation ~
            scale(zips$D2B_E8MIXA) +
            scale(zips$median_household_income) + 
            scale(zips$population_density) + 
            scale(zips$total_population_2) +
            scale(zips$diversity) +
            scale(zips$college_rates) +
            scale(zips$unemployment_rate))


table <- stargazer(lm1, lm2, lm3, lm4, lm5)
```

# Correlate Entertainment Density with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(zips$segregation ~ scale(zips$D1C8_ENT))
lm2 <- lm(zips$segregation ~ scale(zips$D1C8_ENT) + scale(zips$median_household_income))
lm3 <- lm(zips$segregation ~ scale(zips$D1C8_ENT) + scale(zips$population_density))
lm4 <- lm(zips$segregation ~ scale(zips$D1C8_ENT) + scale(zips$median_household_income) + scale(zips$population_density))
lm5 <- lm(zips$segregation ~
            scale(zips$D1C8_ENT) +
            scale(zips$median_household_income) + 
            scale(zips$population_density) + 
            scale(zips$total_population_2) +
            scale(zips$diversity) +
            scale(zips$college_rates) +
            scale(zips$unemployment_rate))


table <- stargazer(lm1, lm2, lm3, lm4, lm5)
```



#Include Fixed Effects
# Correlate intersection density with segregation with different specifications
# Create summary table

```{r}
lm1 <- lm(segregation ~ D3B, data = zips)
lm2 <- lm(segregation ~ D3B + median_household_income, data = zips)
lm3 <- lm(segregation ~ D3B + population_density, data = zips)
lm4 <- lm(segregation ~ D3B + median_household_income + population_density, data = zips)
lm5 <- lm(segregation ~
            D3B +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate,
            data = zips)

lm6 <- lm(segregation ~
            D3B +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate +
            factor(county),
            data = zips)

table <- stargazer(lm1, lm2, lm3, lm4, lm5, lm6)
```

# Correlate Employment Entropy with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(segregation ~ D2B_E8MIXA, data = zips)
lm2 <- lm(segregation ~ D2B_E8MIXA + median_household_income, data = zips)
lm3 <- lm(segregation ~ D2B_E8MIXA + population_density, data = zips)
lm4 <- lm(segregation ~ D2B_E8MIXA + median_household_income + population_density, data = zips)
lm5 <- lm(segregation ~
            D2B_E8MIXA +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate,
            data = zips)

lm6 <- lm(segregation ~
            D2B_E8MIXA +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate +
            as.factor(county),
            data = zips)

table <- stargazer(lm1, lm2, lm3, lm4, lm5, lm6)
```

# Correlate Entertainment Density with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(segregation ~ D1C8_ENT, data = zips)
lm2 <- lm(segregation ~ D1C8_ENT + median_household_income, data = zips)
lm3 <- lm(segregation ~ D1C8_ENT + population_density, data = zips)
lm4 <- lm(segregation ~ D1C8_ENT + median_household_income + population_density, data = zips)
lm5 <- lm(segregation ~
            D1C8_ENT +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate,
            data = zips)

lm6 <- lm(segregation ~
            D1C8_ENT +
            median_household_income + 
            population_density + 
            total_population_2 +
            diversity +
            college_rates +
            unemployment_rate +
            as.factor(county),
            data = zips)

table <- stargazer(lm1, lm2, lm3, lm4, lm5, lm6)
```


# Urban Form colinearity
```{r}
ggplot(zips,aes(x=D3B,y=D1C8_ENT)) + 
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") + 
  ylab("Entertainment Place Density")  
ggsave("urban_form_collinearity_1.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")

ggplot(zips,aes(x=D3B,y=D2B_E8MIXA)) + 
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") + 
  ylab("Employment Entropy")  
ggsave("urban_form_collinearity_2.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")

ggplot(zips,aes(x=D2B_E8MIXA,y=D1C8_ENT)) + 
  stat_summary_bin(fun.y = mean, bins=50,
                   color='black', size=2, geom='point', alpha=0.5) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Employment Entropy") + 
  ylab("Entertainment Place Density")  
ggsave("urban_form_collinearity_3.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```



```{r}
# create color palette 
pal <- colorNumeric(
  palette = "Greens",
  domain = zips@data$segregation)

# create labels for zipcodes
labels <- 
  paste0(
    "Zip Code: ",
    zips$zip, "<br/>",
    "Mean Income: ",
    scales::dollar(zips$segregation)) %>%
  lapply(htmltools::HTML)

zips %>% 
  leaflet %>% 
  # add base map
  addProviderTiles("CartoDB") %>% 
  # add zip codes
  addPolygons(fillColor = ~pal(segregation),
              weight = 2,
              opacity = 1,
              color = "white",
              dashArray = "3",
              fillOpacity = 0.7,
              highlight = highlightOptions(weight = 2,
                                           color = "#666",
                                           dashArray = "",
                                           fillOpacity = 0.7,
                                           bringToFront = TRUE),
              label = labels) %>%
  # add legend
  addLegend(pal = pal, 
            values = ~segregation, 
            opacity = 0.7, 
            title = htmltools::HTML("Mean Income <br> 
                                    Tax Returns <br> 
                                    by Zip Code <br>
                                    2016"),
            position = "bottomright")

```


```{r}
library(sf) #Overall handling of sf objects
library(cartography) #Plotting maps package

#1. Create your data
yourdata <- data.frame(ZCTA5CE10=zips$zip,
                    Cases=zips$bias_grp_mem_zip)

#2. Download a shapefile (shp,gpkg,geojson...)
library(tigris) #For downloading the zipcode map
options(tigris_use_cache = TRUE)
geo <- st_as_sf(zctas(cb = TRUE, starts_with = yourdata$ZCTA5CE10))

#Overall shape of USA states
states <- st_as_sf(states(cb=TRUE))
#For plotting, all the maps should have the same crs
states=st_transform(states,st_crs(geo))

#3. Now Merge your data
yourdata.sf=merge(geo,yourdata)

#4. Plotting
par(mar=c(1,1,1,1))
ghostLayer(yourdata.sf)
plot(st_geometry(states), add=TRUE)
choroLayer(yourdata.sf,
           var="Cases",
           add=TRUE,
           border = NA,
           legend.pos = "right",
           legend.frame = TRUE)
layoutLayer(title = "Cases by ZIPCODE",
            theme = "blue.pal",
            scale = FALSE,
            sources = "Source; your question on SO",
            author = "by dieghernan, 2020"
            )
```
```{r}
library(ggmap)
map<-get_map(location='united states', zoom=4, maptype = "terrain",
             source='google',color='color')
```



