---
title: "Urban Design vs Social Capital"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(jtools)
library(stargazer)
library(datawizard)

rm(list = ls())
setwd("~/Desktop/Thesis")
data <- read.csv("Data/working/data_merged.csv")
cuebiq <- read.csv("Data/working/cuebiq_zip.csv")
data = subset(data, urban == 1)
```

# Create Figure
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          scale(log(Median_Household_Income_2020)) + 
          scale(log(popdensity2010)) +
          scale(D3B) +
          scale(D2B_E8MIXA) +
          scale(NatWalkInd),
          data = data)
  return(model)
}

plot_summs(estimate_horserace_regression(data$bias_grp_mem_county), estimate_horserace_regression(data$ec_county),
           estimate_horserace_regression(data$exposure_grp_mem_county),

           coefs = c("Household Income" = "scale(log(Median_Household_Income_2020))",
                     "Population Density" = "scale(log(popdensity2010))",
                     "Street Intersection Density" = "scale(D3B)",
                     "Employment Entropy" = "scale(D2B_E8MIXA)",
                     "Walkability Index" = "scale(NatWalkInd)"
                     ),

           robust = list("HC0","HC0", "HC0"),
           model.names =c("Friending Bias", "Economic Connectedness", "Exposure"))

# ggsave("features_density_horse_race.pdf", path = "/Users/georgecrowne/Desktop/Thesis/figs")
```

# Create Summary Table
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(outcome ~
          log(Median_Household_Income_2020) + 
          log(popdensity2010) +
          D3B +
          D2B_E8MIXA +
          NatWalkInd,
          data = data)
  return(model)
}

lm1 <- estimate_horserace_regression(data$ec_county)
lm2 <- estimate_horserace_regression(data$bias_grp_mem_county)
lm3 <- estimate_horserace_regression(data$exposure_grp_mem_county)

mean_ec <- round(mean(data$ec_county, na.rm = TRUE), 3)
mean_bias <- round(mean(data$bias_grp_mem_county, na.rm = TRUE), 3)
mean_exp <- round(mean(data$exposure_grp_mem_county, na.rm = TRUE), 3)

sd_ec <- round(sd(data$ec_county, na.rm=TRUE), 3)
sd_bias <- round(sd(data$bias_grp_mem_county, na.rm=TRUE), 3)
sd_exp <- round(sd(data$exposure_grp_mem_county, na.rm=TRUE), 3)

table <- stargazer(lm1, lm2, lm3,
          title="Urban Design vs Social Capital",
          dep.var.labels="Economic Connectedness & Friending Bias & High-SES Exposure",
          covariate.labels=c(
            "Household Income",
            "Population Density",
            "Street Intersection Density",
            "Employment Entropy",
            "Walkability Index"
            ),
          add.lines = list(c("Mean", mean_ec, mean_bias, mean_exp), c("Std. Dev", sd_ec, sd_bias, sd_exp)),
          table.placement="p"
          )

write(table, file="/Users/georgecrowne/Desktop/Thesis/tables/table8.txt")
```

# Get Experienced Segregation and number of visits for each county
```{r}
cols = cuebiq %>% select(
  county,
  state...14,
  nstays,
  segregation
)

counties <- cols %>% 
  group_by(county, state...14) %>% 
  summarize(across(c(segregation),function (x) weighted.mean(x, w=nstays, na.rm=TRUE)))

counties_nstays <- cols %>% 
  group_by(county, state...14) %>% 
  summarize_at(vars(nstays), funs(mean))

# Accounts for DC/Maryland & Virginia issue
# data[data$state_fips == 24,]$state_fips = 11
# data[data$state_fips == 51,]$state_fips = 11


counties <- rename(counties, "name" = "county")
counties <- rename(counties, "state_fips" = "state...14")
counties_nstays <- rename(counties_nstays, "name" = "county")
counties_nstays <- rename(counties_nstays, "state_fips" = "state...14")

counties <- counties %>%
  left_join(data, by = c("name", "state_fips"))

counties_nstays <- counties_nstays %>%
  left_join(data, by = c("name", "state_fips"))

counties <- subset(counties, !is.na(counties$ec_county))
counties_nstays <- subset(counties_nstays, !is.na(counties_nstays$ec_county))

head(counties)

```

# Don't worry about this
```{r}
estimate_horserace_regression = function(outcome) {
  model <- lm(scale(outcome) ~
          scale(log(Median_Household_Income_2020)) + 
          scale(log(popdensity2010)) +
          scale(D3B) +
          scale(D2B_E8MIXA) +
          scale(NatWalkInd),
          data = counties)
  return(model)
}

plot_summs(estimate_horserace_regression(counties$bias_grp_mem_county), estimate_horserace_regression(counties$ec_county),
           estimate_horserace_regression(counties$exposure_grp_mem_county),

           coefs = c("Household Income" = "scale(log(Median_Household_Income_2020))",
                     "Population Density" = "scale(log(popdensity2010))",
                     "Street Intersection Density" = "scale(D3B)",
                     "Employment Entropy" = "scale(D2B_E8MIXA)",
                     "Walkability Index" = "scale(NatWalkInd)"
                     ),

           robust = list("HC0","HC0", "HC0"),
           model.names =c("Friending Bias", "Economic Connectedness", "Exposure"))
```

# Plot segregation against employment entropy
```{r}
ggplot(counties,aes(x=D2B_E8MIXA,y=bias)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Employment Entropy") +
  ylab("Experienced Segregation")

summary(lm(counties$bias ~ counties$D2B_E8MIXA))
```

# Plot segregation against intersection density
```{r}
ggplot(counties,aes(x=D3B,y=segregation)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") +
  ylab("Experienced Segregation")

summary(lm(counties$segregation ~ counties$D3B))
```

# Plot segregation against intersection density
```{r}
ggplot(counties,aes(x=D3B,y=bias)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") +
  ylab("Experienced Segregation")

summary(lm(counties$bias ~ counties$D3B))
```

# Plot segregation against entertainment place density
```{r}
ggplot(counties,aes(x=log(D1C8_ENT),y=segregation)) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Entertainment Job Density") +
  ylab("Experienced Segregation")


summary(lm(counties$segregation ~ counties$D1C8_ENT + counties$pop_2019))
summary(lm(scale(segregation)~scale(D1C8_ENT), data=counties))
summary(lm(scale(segregation)~scale(log(D1C8_ENT))+I(scale(log(D1C8_ENT))^2), data=counties))

```

# Correlate intersection density with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(counties$segregation ~ scale(counties$D3B))
lm2 <- lm(counties$segregation ~ scale(counties$D3B) + scale(counties$Median_Household_Income_2020))
lm3 <- lm(counties$segregation ~ scale(counties$D3B) + scale(counties$pop_density))
lm4 <- lm(counties$segregation ~ scale(counties$D3B) + scale(counties$Median_Household_Income_2020) + scale(counties$pop_density))
lm5 <- lm(counties$segregation ~
            scale(counties$D3B) + 
            scale(counties$Median_Household_Income_2020) + 
            scale(counties$pop_density) + 
            scale(counties$repshare2016) + 
            scale(counties$pct_gte_college_2016_20) + 
            scale(counties$oi_diversity) + 
            scale(counties$Unemployment_rate_2021))

table <- stargazer(lm1, lm2, lm3, lm4, lm5)
```

# Correlate Employment Entropy with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(scale(counties$segregation) ~ scale(counties$D2B_E8MIXA))
lm2 <- lm(scale(counties$segregation) ~ scale(counties$D2B_E8MIXA) + scale(counties$Median_Household_Income_2020))
lm3 <- lm(scale(counties$segregation) ~ scale(counties$D2B_E8MIXA) + scale(counties$pop_density))
lm4 <- lm(scale(counties$segregation) ~ scale(counties$D2B_E8MIXA) + scale(counties$Median_Household_Income_2020) + scale(counties$pop_density))
lm5 <- lm(scale(counties$segregation) ~
            scale(counties$D2B_E8MIXA) + 
            scale(counties$Median_Household_Income_2020) + 
            scale(counties$pop_density) + 
            scale(counties$repshare2016) + 
            scale(counties$pct_gte_college_2016_20) + 
            scale(counties$oi_diversity) + 
            scale(counties$Unemployment_rate_2021))

table <- stargazer(lm1, lm2, lm3, lm4, lm5)
```

# Correlate Entertainment Job Density with segregation with different specifications
# Create summary table
```{r}
lm1 <- lm(scale(counties$segregation) ~ scale(counties$D1C8_ENT))
lm2 <- lm(scale(counties$segregation) ~ scale(counties$D1C8_ENT) + scale(counties$Median_Household_Income_2020))
lm3 <- lm(scale(counties$segregation) ~ scale(counties$D1C8_ENT) + scale(counties$pop_density))
lm4 <- lm(scale(counties$segregation) ~ scale(counties$D1C8_ENT) + scale(counties$Median_Household_Income_2020) + scale(counties$pop_density))
lm5 <- lm(scale(counties$segregation) ~
            scale(counties$D1C8_ENT) + 
            scale(counties$Median_Household_Income_2020) + 
            scale(counties$pop_density) + 
            scale(counties$repshare2016) + 
            scale(counties$pct_gte_college_2016_20) + 
            scale(counties$oi_diversity) + 
            scale(counties$Unemployment_rate_2021))

table <- stargazer(lm1, lm2, lm3, lm4, lm5)

```

# Does urban design create more visits to places?

# Correlate intersection density with number of visits
```{r}
ggplot(counties_nstays,aes(x=D3B,y=nstays)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") +
  ylab("Num Visits")

summary(lm(counties_nstays$nstays ~ counties_nstays$D3A))
```

# Correlate employment entropy with number of visits
```{r}
ggplot(counties_nstays,aes(x=D2B_E8MIXA,y=nstays)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Employment Entropy") +
  ylab("Num Visits")

summary(lm(counties_nstays$nstays ~ counties_nstays$D2B_E8MIXA))
```

# Correlate entertainment place density with number of visits
```{r}
ggplot(counties_nstays,aes(x=log(D1C8_ENT),y=nstays)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Entertainment place density") +
  ylab("Num Visits")

summary(lm(counties_nstays$nstays ~ counties_nstays$D1C8_ENT))
```

# Plot Cuebiq county level data
```{r}
ggplot(counties, aes(x=segregation)) + 
  geom_histogram() +
  geom_density(alpha=.2, fill="#FF6666")
```

# Get segregation as percentile of national distribution
```{r}
df <- data.frame(counties)
df$segregation_percentile = df$segregation

df <- mutate(df, segregation_percentile = ntile(df$segregation,100))
```

# Get urban design measures as percentile of national distribution
```{r}
df$intersection_percentile = df$D3B
df$employment_entropy_percentile = df$D2B_E8MIXA
df$entertainment_percentile = df$D1C8_ENT

df <- mutate(df, intersection_percentile = ntile(df$D3B,100))
df <- mutate(df, employment_entropy_percentile = ntile(df$D2B_E8MIXA,100))
df <- mutate(df, entertainment_percentile = ntile(df$D1C8_ENT,100))
```

# Plot entertainment density against segregation percentile
```{r}
ggplot(df,aes(x=entertainment_percentile,y=segregation_percentile)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Entertainment place density") +
  ylab("Experienced Income segregation")

summary(lm(df$segregation_percentile ~ df$entertainment_percentile))
```

# Plot intersection density against segregation percentile
```{r}
ggplot(df,aes(x=intersection_percentile,y=segregation_percentile)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Intersection Density") +
  ylab("Segregation Percentile")

summary(lm(df$segregation_percentile ~ df$intersection_percentile))
```

# Plot intersection density against segregation percentile
```{r}
ggplot(df,aes(x=employment_entropy_percentile,y=segregation_percentile)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Employment Entropy") +
  ylab("Segregation Percentile")

summary(lm(df$segregation_percentile ~ df$employment_entropy_percentile))
```

# Winsorize values
```{r}
df$winsorize_segregation = df$segregation
winsorize(df$winsorize_segregation, probs = c(0.05, 0.95))

df$winsorize_intersection = df$D3B
winsorize(df$winsorize_intersection, probs = c(0.05, 0.95))
df$winsorize_employment_entropy = df$D2B_E8MIXA
winsorize(df$winsorize_employment_entropy, probs = c(0.05, 0.95))
df$winsorize_entertainment = df$D1C8_ENT
winsorize(df$winsorize_entertainment, probs = c(0.05, 0.95))

```

# Correlate Winsorized segregation with winsorized intersection density
```{r}
ggplot(df,aes(x=winsorize_intersection,y=winsorize_segregation)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method='lm',formula=y~x) +
  xlab("Entertainment place density") +
  ylab("Experienced Income segregation")

summary(lm(df$winsorize_segregation ~ log(df$winsorize_intersection)))
```

# See if urban form associates with other social capital outcomes
# Volunteering Rates
```{r}
summary(lm(volunteering_rate_county ~ D3B + D1C8_ENT + D2B_E8MIXA, data = data))
```

# Civic Organizations
```{r}
summary(lm(civic_organizations_county ~ D3B + D1C8_ENT + D2B_E8MIXA + pop_density , data = data))
```

